\documentclass[letterpaper,10pt]{article}

\usepackage{makecell}
\usepackage[link=off]{phonenumbers}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\usepackage[margin=0.3in]{geometry}
% Adjust margins
\addtolength{\oddsidemargin}{-0.0in}
\addtolength{\evensidemargin}{-0.0in}
\addtolength{\textwidth}{0in}
\addtolength{\topmargin}{20pt}
\addtolength{\textheight}{0.0in}

\urlstyle{same}

\usepackage{xcolor}% http://ctan.org/pkg/xcolor
\usepackage{hyperref}% http://ctan.org/pkg/hyperref
\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!red,
  linkbordercolor=red,
  urlcolor=blue!70!black
}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\def \ifempty#1{\def\temp{#1} \ifx\temp\empty }

\newcommand{\resumeItem}[2]{
  \item\small{
  	\ifempty{#1}#2\else\textbf{#1}{: #2 \vspace{-2pt}}\fi
  }
}

\usepackage[dvipsnames]{xcolor}
\definecolor{mygray}{gray}{0}
\usepackage{fancybox}

\usepackage{lmodern}
\usepackage{tikz}

% Style definition
\tikzset{rndblock/.style={rounded corners,rectangle,draw,outer sep=0pt}}

% Command Definition
% 1 optional to customize the aspect, 2 mandatory: text to be framed
\newcommand{\tframed}[2][]{\tikz[baseline=(h.base)]\node[rndblock,#1] (h) {\color{black}{#2}};}

\newcommand*{\mystrut}{\rule[-0.2\baselineskip]{0pt}{0.8\baselineskip}}
\newcommand{\skill}[1]{\tframed[lightgray]{\mystrut#1}}


\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textcolor{mygray}{#2} \\
      \textit{\small#3} & \textcolor{mygray}{\textit{\small #4}} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeExpSubheading}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}  & \textcolor{mygray}{#2} \\
      \textit{\small#3} & \textcolor{mygray}{\textit{\small #4}} \\
      {\scriptsize#5}
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeProjSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1}  & \textcolor{mygray}{#2} \\
      \scriptsize {#3} & \textcolor{mygray}{\textit{\small #4}} \\
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\usepackage{changepage}
\newcommand{\resumeDesc}[1]{\begin{adjustwidth}{5pt}{0pt}\vspace{-2pt}{\small{#1}}\end{adjustwidth}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Alexander Atalyan} & Email: \href{mailto:sasha.atalyan@gmail.com}{sasha.atalyan@gmail.com}\\
  Github: \href{https://github.com/PotatoCoder228}{PotatoCoder228} & Mobile: +7\hspace{0.5ex}988\hspace{0.5ex}862\hspace{0.5ex}85\hspace{0.5ex}32 \\
  {St. Petersburg, Russia}
\end{tabular*}

\section{Objective}
    \vspace{0.5 em}
        \resumeDesc{\hspace{0.3 em} I am looking for an entry-level position in the field of computer science, where I could apply my technical
        skills and acquired knowledge.\hspace{0.3 em}}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
       {ITMO University}{Sept. 2021 -- Present}
      {Bachelor of Software Engineering}{GPA: 4.5/5.0}
    \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart
  
      \resumeProjSubheading
      {\href{https://github.com/PotatoCoder228/CountMathLab1}{Console Application}}{St. Petersburg, Russia}
      {\skill{C}}{Feb. 2023}
          \resumeDesc{Console application that implements Gauss method for linear equations solving.
          Generic vector and single linked list containers were written for implementations, in addition an error handler and a small wrapper for interacting with strings were developed.}
  
    \resumeProjSubheading
      {\href{https://github.com/PotatoCoder228/Web_Lab_4}{Single Page Application based on Spring Framework and React.js}}{St. Petersburg, Russia}
      {\skill{Java SE} \skill{Spring Boot}
      \skill{Spring Data}
      \skill{Spring Security}
      \skill{JavaScript} \skill{React.js} \skill{PostgreSQL} \skill{HTML} \skill{CSS}}{Jan. 2023}
          \resumeDesc{Web application for calculating the hit of a point in the area. The back-end was written on Spring, the front-end was written on React.js. For interaction with users, registration, authorization and an interactive area with a table of results have been developed. The results are stored in a PostgreSQL database. The interaction between the back-end and front-end is organized
          through the REST API.}
    \resumeProjSubheading
      {\href{https://github.com/DmitryLedentsov/electric-field}{Electric field visualization application}}{St. Petersburg, Russia}
      {\skill{Java SE}  \skill{JavaFX} \skill{Gradle}
      }{Dec. 2022}
          \resumeDesc{Participated in the development of university physics project in team (2 participants). This is a GUI application that allows users to place positive or negative charges and planes on an interactive field and observe changes in the electric field strength lines and the equipotential line.}
    \resumeProjSubheading
      {\href{https://github.com/PotatoCoder228/Lab_7}{Multithreaded client-server application}}{St. Petersburg, Russia}
      {\skill{Java SE}  \skill{PostgreSQL} \skill{JDBC} \skill{Maven} \skill{Log4j2}}{Jun. 2022}
          \resumeDesc{A client-server application that implements the management of a collection of objects. The server module receives and executes commands that control the collection from a non-block TCP connection. The data is stored in a PostgreSQL database. A JDBC driver is used to interact with the database. The client module reads commands in multi threaded interactive mode, sends them to the server for execution and prints the results of execution.}

      
  \resumeSubHeadingListEnd
%
%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Programming}{: C, Java SE, Java EE, JavaScript, HTML, CSS, Bash, SQL (Beginner) }
   }\vspace{-7pt}
   \item{
     \textbf{Technologies}{: Make, CMake, Maven, Git, Spring Boot, Spring Data, JDBC, WildFly, React.js (Beginner), \LaTeX }
   }
   \vspace{-7pt}
   \item{
     \textbf{Languages}{: Russian (Native), English (Pre-Intermediate)}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
